### 2018-10-09 Sections/errors_in_quantum_networks.tex

The degree of amplitude damping is often quoted in terms of a channel's $T_1$-time, characterising the expected time for the excited state to undergo spontaneous emission and relax to the ground state. Using this parameterisation we can express the amplitude damping channel as,
\begin{align}
\mathcal{E}_t^\mathrm{relax}(\hat\rho) = e^{-t/T_1}\hat\rho + (1-e^{-t/T_1})\ket{0}\bra{0},
\end{align}
for which the output state is of the form,
\begin{align}
\hat\rho_t = \left(\begin{matrix}{}
1 + (\alpha-1) e^{-t/T_1} & \gamma e^{-t/T_1} \\
\gamma^* e^{-t/T_1} & \beta e^{-t/T_1}
\end{matrix}\right).
\end{align}

>>>>

The degree of amplitude damping is often quoted in terms of a channel's $T_1$-time\index{T$_1$-time}, characterising the expected time for the excited state to undergo spontaneous emission and relax to the ground state. Using this parameterisation we can express the amplitude damping channel as,
\begin{align}
\mathcal{E}_t^\mathrm{relax}(\hat\rho) = e^{-t/T_1}\hat\rho + (1-e^{-t/T_1})\ket{0}\bra{0},
\end{align}
for which the output state is of the form,
\begin{align}
\hat\rho_t = \left(\begin{matrix}{}
1 + (\alpha-1) e^{-t/T_1} & \gamma e^{-t/T_1} \\
\gamma^* e^{-t/T_1} & \beta e^{-t/T_1}
\end{matrix}\right).
\end{align}

### 2018-10-09 Sections/statement_of_contributions.tex
minor

\begin{itemize}
\item P.P.R conceived and directed this project, developed the original ideas, and prepared most of the manuscript.
\item Z.E.S \& H.L.H prepared Sec.~\ref{sec:state_of_the_art}.
\item W.J.M prepared Sec.~\ref{sec:rep_net}. 
\item R.L.M contributed to Sec.~\ref{sec:protocols_quant_int}.
\item T.B \& J.P.D wrote Sec.~\ref{sec:quant_space_race}.
\item Z.H contributed to Secs.~\ref{sec:cryptowars}, \ref{sec:CV_QC}
\item C.F \& N.L wrote Sec.~\ref{sec:quantum_mind}.
\item N.L wrote Sec.~\ref{sec:verification}.
\item All authors played active roles in the discussions that developed this work. 
\end{itemize}

\comment{Add everyone else}

>>>>

\begin{itemize}
\item Peter P. Rohde conceived, directed and edited this project, developed the original ideas, and prepared most of the manuscript.
\item Zixin Huang wrote Secs.~\ref{sec:telescopy}, \ref{sec:CV_QC}, \ref{sec:essay_future_QKD}.
\item Zuen Su \& Heliang Huang prepared Part~\ref{part:SotA}.
\item William J. Munro prepared Sec.~\ref{sec:rep_net}. 
%\item Ryan L. Mann contributed to Sec.~\ref{sec:protocols_quant_int}.
\item Scott Harrison wrote Secs.~\ref{sec:econ_prop}, \ref{sec:policy} \& \ref{sec:game_theory}.
\item Tim Byrnes \& Jonathan P. Dowling wrote Sec.~\ref{sec:quant_space_race}.
\item Nana Liu \& Chris Ferrie wrote Sec.~\ref{sec:quantum_mind}.
\item Nana Liu wrote Sec.~\ref{sec:verification}.
\item All authors played active roles in the discussions that developed this work. 
\end{itemize}

\comment{Add everyone else}
\comment{Put in same order as authorship}

### 2018-10-09 Sections/the_quantum_space_race.tex

However, extending to longer distances has been problematic. Photon loss in free space links is affected by weather\index{Weather conditions} conditions and other atmospheric effects\index{Atmospheric effects}\index{Photon loss}, such as pollution\index{Pollution}, which degrade visibility. The Earth's curvature\index{Earth curvature} provides an absolute upper limit, depending on the elevation of the source and receiver. For example, for an observer on a 30m tower, the horizon is at a distance of 20km, a relatively short distance. The observatory used in the experiments performed by the experiments of \cite{bib:ursin07, bib:ma2012quantum} were at an elevation of 2393m, allowing transmission over a distance of 143km.

>>>>

However, extending to longer distances has been problematic. Photon loss in free-space links is affected by weather\index{Weather conditions} conditions and other atmospheric effects\index{Atmospheric effects}\index{Photon loss}, such as pollution\index{Pollution}, which degrade visibility. The Earth's curvature\index{Earth curvature} provides an absolute upper limit, depending on the elevation of the source and receiver. For example, for an observer on a 30m tower, the horizon is at a distance of 20km, a relatively short distance. The observatory used in the experiments performed by the experiments of \cite{bib:ursin07, bib:ma2012quantum} were at an elevation of 2393m, allowing transmission over a distance of 143km.
